---
title: "Explanatory Data Analysis"
author: "Turjya Laskar"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Library used:

In this report, several R libraries were utilized to facilitate data analysis and presentation.

- **DT**: Used for creating interactive data tables.
- **tidyverse**: A suite of packages for data manipulation and visualization.
- **glue**: Facilitates string interpolation for dynamic text outputs.

```{r library, warning=F, message=FALSE}
library(DT)
library(tidyverse)
library(glue)
```

## Data Loading

```{r data, message=FALSE}

train_features <- read_csv("C:/Users/Lenovo/Desktop/Kaggle Project/Dataset/train_features.csv", show_col_types = FALSE)
train_drug <- read_csv("C:/Users/Lenovo/Desktop/Kaggle Project/Dataset/train_drug.csv", show_col_types = FALSE)
train_target_nonscored<-read_csv("C:/Users/Lenovo/Desktop/Kaggle Project/Dataset/train_targets_nonscored.csv", show_col_types = FALSE)
train_taret_scored<- read_csv("C:/Users/Lenovo/Desktop/Kaggle Project/Dataset/train_targets_scored.csv",  show_col_types = FALSE)
sample_submission <- read_csv("C:/Users/Lenovo/Desktop/Kaggle Project/Dataset/sample_submission.csv",  show_col_types = FALSE)
```

## Expalnatory Data Analysis

To start, we’ll get a quick overview of the  *train_features* datasets and their shapes.

```{r train_features, echo=FALSE}

head(train_features,50)%>%
  datatable()
```

Here,

- **sig_id**: Used for creating interactive data tables.
- **cp_type**: indicates the sample treatment.
- **cp_time**: indicates duration of the treatment.
- **cp_dose**: indicates dosage of the treatment.
- **'g-'**: Gene expression data.
- **'c-'**: cell viability data.
 
### Shape of the **train_features**

```{r shape, echo=FALSE}
glue(
"Number of rows: {nrow(train_features)}\nNumber of columns: {ncol(train_features)}"
)
```
### Number of 'g-' & 'c-' features
```{r gene&cell, echo=FALSE}
glue(
'Number of "g-" features: {train_features %>% select(starts_with("g-"))%>%ncol()}\nNumber of "c-" features: {train_features %>% select(starts_with("c-"))%>%ncol()}'
)
```
### Number of Unique sid_ids
```{r unique id, echo=FALSE}
glue('Total number of unique sig_ids: {n_distinct(train_features$sig_id)}')
```

```{r cp_type, echo=FALSE}
train_features%>%
  group_by(cp_type)%>%
  summarise(count=n())%>%
  datatable()
```
```{r cp_time, echo=FALSE}
train_features%>%
  group_by(cp_time)%>%
  summarise(count=n())%>%
  datatable()
```
```{r cp_dose,echo=FALSE}
train_features%>%
  group_by(cp_dose)%>%
  summarise(count=n())%>%
  datatable()

```
## Conclusion














