---
title: "Explanatory Data Analysis"
author: "Turjya Laskar"
date: "`r Sys.Date()`"
output: 
  html_document:
    toc: yes
    number_sections: yes
    toc_float:
      collapsed: no
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## **Library used**:

In this report, several R libraries were utilized to facilitate data analysis and presentation.

- **DT**: Used for creating interactive data tables.
- **tidyverse**: A suite of packages for data manipulation and visualization.
- **glue**: Facilitates string interpolation for dynamic text outputs.

```{r library, warning=F, message=FALSE}
library(DT)
library(tidyverse)
library(glue)
library(ggthemes)
library(scales)
library(RColorBrewer)
```

## **Data Loading**

```{r data, message=FALSE}

train_features <- read_csv("C:/Users/Lenovo/Desktop/Kaggle Project/Dataset/train_features.csv", show_col_types = FALSE)
train_drug <- read_csv("C:/Users/Lenovo/Desktop/Kaggle Project/Dataset/train_drug.csv", show_col_types = FALSE)
train_target_nonscored<-read_csv("C:/Users/Lenovo/Desktop/Kaggle Project/Dataset/train_targets_nonscored.csv", show_col_types = FALSE)
train_taret_scored<- read_csv("C:/Users/Lenovo/Desktop/Kaggle Project/Dataset/train_targets_scored.csv",  show_col_types = FALSE)
sample_submission <- read_csv("C:/Users/Lenovo/Desktop/Kaggle Project/Dataset/sample_submission.csv",  show_col_types = FALSE)
```

## **Explanatory Data Analysis**

To start, we’ll get a quick overview of the  *train_features* datasets and their shapes.

```{r train_features, echo=FALSE}

head(train_features,50)%>%
  datatable()
```

Here,

- **sig_id**: Used for creating interactive data tables.
- **cp_type**: indicates the sample treatment.
- **cp_time**: indicates duration of the treatment.
- **cp_dose**: indicates dosage of the treatment.
- **'g-'**: Gene expression data.
- **'c-'**: cell viability data.
 
### Shape of the train_features

```{r shape, echo=FALSE}
glue(
"Number of rows: {nrow(train_features)}\nNumber of columns: {ncol(train_features)}"
)
```
### Number of 'g-' & 'c-' features
```{r gene&cell, echo=FALSE}
glue(
'Number of "g-" features: {train_features %>% select(starts_with("g-"))%>%ncol()}\nNumber of "c-" features: {train_features %>% select(starts_with("c-"))%>%ncol()}'
)
```
### Number of Unique sid_ids
```{r unique id, echo=FALSE}
glue('Total number of unique sig_ids: {n_distinct(train_features$sig_id)}')
```

## Individual Treatment Features {.tabset}

### Treatment Type
```{r cp_type, echo=FALSE}
train_features%>%
  group_by(cp_type)%>%
  summarise(count=n())%>%
  datatable()
```

```{r cp_type_viz, echo=FALSE}
p1 <- train_features %>% 
  count(cp_type) %>% 
  add_tally(n, name = "total") %>% 
  mutate(perc = n / total) %>% 
  ggplot(aes(x = cp_type, y = perc, fill = cp_type)) +
  geom_col(width = 0.6) +
  geom_text(aes(label = sprintf("%d", n)), vjust = -0.5, size = 5, color = "black") +
  scale_y_continuous(labels = percent_format(), expand = expansion(mult = c(0, 0.1))) +
  scale_fill_manual(values = c("grey70", "violetred")) +
  theme_hc() +
  theme(
    legend.position = "none",
    plot.title = element_text(size = 14, face = "bold", hjust = 0.5),
    plot.subtitle = element_text(size = 12, hjust = 0.5),
    axis.text.x = element_text(size = 12),
    axis.text.y = element_text(size = 12),
    axis.ticks = element_blank(),
    panel.grid.major.y = element_line(color = "grey80"),
    panel.grid.minor = element_blank()
  ) +
  labs(
    x = NULL,
    y = NULL,
    title = "Sample Treatment",
    subtitle = "(Compound vs Control)"
  )

p1

```


### Treatment Duration
```{r cp_time, echo=FALSE}
train_features%>%
  group_by(cp_time)%>%
  summarise(count=n())%>%
  datatable()
```

```{r cp_time_viz,echo=FALSE}

p2 <- train_features %>%
  count(cp_time) %>%
  mutate(cp_time = as.factor(cp_time)) %>%
  add_tally(n, name = "total") %>%
  mutate(perc = n / total) %>%
  ggplot(aes(x = cp_time, y = perc, fill = cp_time)) +
  geom_col(width = 0.6) +
  geom_text(aes(label = sprintf("%d", n)), vjust = -0.5, size = 5, color = "black") +
  scale_y_continuous(labels = percent_format(), expand = expansion(mult = c(0, 0.1))) +
  scale_fill_brewer(type = "seq", palette = "Oranges") +
  theme_hc() +
  theme(
    legend.position = "none",
    plot.title = element_text(size = 14, face = "bold", hjust = 0.5),
    plot.subtitle = element_text(size = 12, hjust = 0.5),
    axis.text.x = element_text(size = 12),
    axis.text.y = element_text(size = 12),
    axis.ticks = element_blank(),
    panel.grid.major.y = element_line(color = "grey80"),
    panel.grid.minor = element_blank()
  ) +
  labs(
    x = NULL,
    y = NULL,
    title = "Treatment Duration",
    subtitle = "(Units of hours)"
  )

p2

```


### Treatment Dose
```{r cp_dose,echo=FALSE}
train_features%>%
  group_by(cp_dose)%>%
  summarise(count=n())%>%
  datatable()

```
```{r cp_dose_viz, echo=FALSE}
p3 <- train_features %>%
  count(cp_dose) %>%
  add_tally(n, name = "total") %>%
  mutate(perc = n / total) %>%
  ggplot(aes(x = cp_dose, y = perc, fill = cp_dose)) +
  geom_col(width = 0.6) +
  geom_text(aes(label = sprintf("%d", n)), vjust = -0.5, size = 5, color = "black") +
  scale_y_continuous(labels = percent_format(), expand = expansion(mult = c(0, 0.1))) +
  scale_fill_manual(values = c("darkblue", "darkred")) +
  theme_hc() +
  theme(
    legend.position = "none",
    plot.title = element_text(size = 14, face = "bold", hjust = 0.5),
    plot.subtitle = element_text(size = 12, hjust = 0.5),
    axis.text.x = element_text(size = 12),
    axis.text.y = element_text(size = 12),
    axis.ticks = element_blank(),
    panel.grid.major.y = element_line(color = "grey80"),
    panel.grid.minor = element_blank()
  ) +
  labs(
    x = NULL,
    y = NULL,
    title = "Treatment Dose",
    subtitle = "(High vs Low)"
  )

p3
```




## Conclusion














